\section*{Summary}
\subsection*{Dionyzus Unity3D Game}
This graduate work is a game, made in Unity3D game engine. It is 3D game, open world, sandbox game based of GTA (Grand theft auto) series. This game was made as a demo which shows what can be done in Unity. Purpose of this graduation work is to enjoy and have fun while testing, adding custom story line, as well as programming and adding some original features in world of gaming.
It combines different types of knowledge, it encourages developing of different set of skills such as visuals and animation design, music composing, creating interesting atmosphere, describing characters and story line, all that is necessary to make future player interested in the game as well as connected to it. Throughout the game develop, programmer meets people from different industries with a purpose to gather all kinds of information, it could be anything connected to the game develop, getting feedback when it comes to bugs as well as listening to the different advises etc. With this project it was shown how with no investment it's possible to create a game which offers hours and hours of fun time.
Game shows life of Leon and his path to find out who is behind the set-up in which his best friend dies. Beside doing tasks and surviving through the challenges which lead to finishing story, player can freely explore the city and do side jobs which aren't related to main story.

Keywords: Game engine Unity which refers to complete Unity, editor and C\# library, framework Unity which refers to C\# library, C\# programming language, Dionyzus - name of the game, 3D game - game in 3 dimensions.